Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-04 draft.tex
sketch of argument about calculus

\owen{Explain why there is a canonical map from the fact hlgy of a center to the center of the fact hlgy}

\begin{prp}
For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
the canonical map of $E_k$-algebras
\[
\int_{S} \fZ_n(\fg) \to \fZ_k \left( \int_S \UU_n \fg \right)
\]
is a weak equivalence.
\end{prp}

@@

\begin{qtn}
Is the canonical map always a weak equivalence?
\end{qtn}

@@

>>>>

A natural question in our setting is what happens to our pair $(\bZ_n(\fg), \bU_n \fg)$ when we take factorization homology.
As we will see below, the behavior is optimal.

Let us start with a discussion of the general situation.
Let $(A,B)$ be a Swiss cheese pair: $A$ is an $E_1$ algebra in $E_n$ algebras and $B$ is an $E_n$ algebra in left $A$-modules. 
We will freely view these as locally constant factorization algebras on framed $n$-manifolds.
Observe that since factorization homology is a symmetric monoidal functor, 
it is immediate that $\int_S B$ is a left module over $\int_S A$.
Indeed, for any $(n-k)$-dimensional framed manifold $S$, 
taking factorization homology $\int_S B$ yields a locally constant factorization algebra on $\RR^k$ 
and this factorization structure is compatible with the left action of $\int_S A$ as a locally constant factorization algebra on $\RR^k$.
The universal property of the center implies there is then a canonical map
\[
\int_{S} A \to \fZ_k \left( \int_S B \right).
\]
In particular, when $A = \fZ(B)$, we have
\begin{equation}
\label{eqn: can cen int}
\int_{S} \fZ(B) \to \fZ_k \left( \int_S B \right),
\end{equation}
so that taking centers intertwines with taking factorization homology.
In our favorite case, this relationship is as nice as possible.

\begin{prp}
\label{prp: z commutes with int}
For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
the canonical map of $E_k$-algebras
\[
\int_{S} \fZ_n(\fg) \to \fZ_k \left( \int_S \UU_n \fg \right)
\]
is a weak equivalence.
\end{prp}

@@

\begin{qtn}
Is the canonical map \eqref{eqn: can cen int} always a weak equivalence?
\end{qtn}

@@

\begin{proof}[Proof of Proposition~\ref{prp: z commutes with int}]
The key fact is a simple consequence of the K\"unneth theorem in the setting of de Rham forms.
Let $S$ be the closed $n-k$-dimensional manifold of the proposition,
and let $V$ be an arbitrary manifold without boundary.
Then there is a canonical map
\[
\Omega^*(V) \otimes \Omega^*(S) \to \Omega^*(V \times S),
\]
by wedge product after pulling back along the two projection maps.
It is a quasi-isomorphism, by K\"unneth.
Similarly, the canonical map
\[
\Omega_c^*(V) \otimes \Omega^*(S) \to \Omega_c^*(V \times S),
\]
is a quasi-isomorphism, as $S$ is compact.

Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^*(S) \otimes \fg$. 
Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
\begin{align*}
\Omega^*(V) \otimes \fg_S &\xto{\simeq} \Omega^*(V \times S) \otimes \fg \\
\Omega_c^*(V) \otimes \fg_S &\xto{\simeq} \Omega_c^*(V \times S) \otimes \fg 
\end{align*}
and hence a quasi-isomorphism
\[
\bU_k \fg_S \xto{\simeq} \int_S \bU_n \fg
\]
of factorization algebras.

Likewise, on each open set $V \subset \RR^k$, 
we obtain a quasi-isomorphism
\[
\bZ_k(\fg_S)(V) \cong \clies( \Omega^*(V) \otimes \fg_S, \bU_k \fg_S) \xto{\simeq} \clies(\Omega^*(V \times S) \otimes \fg, \bU_n(V \times S))
\]
and this map is functorial in opens.
The righthand side is, however, the pushforward $\int_S \bZ_n \fg$.
\owen{Hmmm, that map goes the wrong way, but I'm pretty sure it provides the inverse-up-to-qiso we need.}
\end{proof}
